\LARGE \bf Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty [v5 Feb 18, 2015 ]

### 2015-02-28 paper.tex
Added ken's feedback

\title{\LARGE \bf
Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Multi-Armed Bandit Models [v3 Feb 12, 2015 ] }

\author{Michael Laskey$^1$,Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
}

@@

\begin{abstract}
\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
\end{abstract}

@@

Consider a robot processing orders in a warehouse, where it frequently encounters new consumer products and must process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of object shape, pose and material properties like friction coefficient or center of mass. 
Furthermore, the robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions or surface properties such as transparency or reflective surfaces.

\begin{figure}%
    \centering
%     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%

%       \qquad

     \subfloat{{\includegraphics[width=8cm]{matlab_figures/pfc.eps} }}%

    \caption{\todo{New teaser photo, not sure if we should have some sort of real object or not}(Top Left) Image of a common household measuring cup. (Top Right) Image from a PR2 Primesense camera that reflects the uncertainty that can be induced in objects from transparency. (Bottom) Comparision of Multi-Armed Bandit Techniques (Bayes UCB, Thompson, Gittins) vs. Monte-Carlo sampling to determine the best grasp in a set of 1000 grasps. As you can see the bandit techniques converge in simple regret Eq. \ref{eq:simple_regret} a magnitude faster than the traditional approach of Monte-Carlo sampling to determine the highest quality grasp.  }%
    \label{fig:rot_shapes}%
\end{figure}

Analytic grasp quality metrics have been developed to determine the stability of a grasp when all the parameters of the object and robot manipulator are exactly known.
One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{}.
Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
Recent works have explored computing the probability of a grasp achieving the force closure condition given uncertainty in parameters such as pose~\cite{christopoulos2007handling, weisz2012pose, kim2012physically} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
Many methods for evaluating grasp quality in the presence of uncertainty use exhaustive Monte-Carlo sampling over the possible values of uncertain quantities~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards} which can be very time consuming.
We are interested in ruling out grasps with a low probability in only a few samples and allocate more sampling effort to grasps that are likely to be high quality.

The multi-armed bandit (MAB) model for sequential decision making problems~\cite{barto1998reinforcement, lai1985asymptotically, robbins1952some} provides a formal way to reason about allocating sampling effort to grasps such that the grasp(s) with highest quality can be determined in as few samples as possible.
In a standard MAB there are a set of possible options (or `arms' in the literature~\cite{barto1998reinforcement}) that each return a numeric reward from a stationary distribution.
The goal in a MAB problem is to sequentially select ones of the possible options such that a measure of expected reward is maximized.
Solutions to the MAB model are particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
The budgeted multi-armed bandit model \cite{madani2004budgeted} is a specialization of the MAB model where an agent has a fixed number of decisions to make before choosing the best option.
The objective is to maximize the expected reward of the decision made at the stopping time, or equivalently to minimize ``simple regret", which is the difference between the true expected reward of an optimal arm and the true expected reward of the arm pulled at the stopping time.

Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem. %\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient. 
We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}. 
Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.

Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
We compare the performance of several popular algorithms for solving the BMAB problem: Thompson sampling, and Gittins indices. 
\todo{Going to fill bottom paragraph in later}
Initial results suggest a promising avenue with a Xx improvement over  the traditional Monte-Carlo integration and Xx improvement in the experiments that we tried.

@@

Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.
A common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves exhaustively sampling from distributions on random quantities and averaging the quality over these samples to approximate an expected value~\cite{caflisch1998monte}.
Exhaustive sampling can be computationally expensive, which motivated the use of Cloud Computing to distribute sampling effort~\cite{kehoe2012toward}.

To further address the computational complexity, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps. However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away.
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty when the robot is able to obtain new information via tactile sensor.
MCMC provides a Bayesian framework for inference with a hidden state, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

 \todo{Michael: should we include this next section on GPIS}
We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.  However, this relied on an approximation to grasp quality without guarantees on accuracy. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.

\section{Preliminaries and Problem Definition}
We consider selecting a grasp on object from a given set of candidate grasps.
We formulate this problem for grasping a planar object from above using parallel-jaw grippers.
We assume that the object is rigid and remains stationary throughout the grasp.
In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient and we assume that distributions on these quantiites are given.
In this section, we formally define our grasping model, formalize our sources of uncertainty, introduce our metric for grasp quality, and finally define our grasp planning objective.

\subsection{Candidate Grasp Model}
Our candidate grasp model is illustrated in Fig.~\ref{fig:grasp_model}.
Let $d$ denote the dimensionality of the shape representations we are using to select grasps and $m$ denote the number of jaws on the robotic gripper.
In this work we formulate the MAB problem for 2-dimensional shapes using parallel-jaw grippers, so $d=2$ and $m=2$.
In this work we also assume a finite width for each parallel jaw $w_j \in \mathbb{R}$.

Similar to~\cite{christopoulos2007handling}, we parameterize a grasp using a {\it line of action} for each gripper jaw, where each line of action is a 1D curve $\gamma(t): [0,1] \rightarrow \mathbb{R}^d$ with endpoints $\gamma(0) = \ba$ and $\gamma(1) = \bb$.
The line of action defines the trajectory that a jaw follows as the gripper closes around a shape.
A {\it grasp plan} is the set of lines of action for each of the jaws, $\Gamma = \{\gamma_1(\cdot),...,\gamma_m(\cdot)\})$ \cite{}.
For parallel-jaw grippers, $\Gamma = \{\gamma(t), \gamma(1 - t)\}$, since the two jaws approach the shape in opposite directions.
Furthermore, in this work we consider only straight lines of action.
The line of action model allows us to compute perturbations to the contact points and normals that occur due to shape uncertainty.
%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changes in the location of contact with a surface, and the line of action allows us to compute these new locations.

Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following the given plan, $\bc_1, ..., \bc_m \in \mathbb{R}^d$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, ..., \bn_m \in \mathbb{R}^d$ and the object center of mass as $\bz \in \mathbb{R}^d$.
Together these form the set of grasp parameters $g = (\bc_1, ..., \bc_m, \bn_1, ... \bn_m, \bz)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object.

\begin{figure}[t!]
\centering
\includegraphics[width = 8cm, height = 6.5cm]{figures/grasp_model.jpg}
\caption{llustration of our grasping model for parallel jaw grippers on a GPIS model of a marker with shape uncertainty near the object center. Jaw placements are illustrated by a red direction arrow and line. The grasp plan consists of a line of action $\gamma(t)$ with endpoints $\ba$ and $\bb$. When following the grasp plan, the jaws contact the shape at locations $\bc_1$ and $\bc_2$ with outward pointing unit surface normals $\bn_1$ and $\bn_2$. Together with the center of mass of the object $\bz$, these values can be used to determine the forces and torques that a grasp can apply to an object. \todo{Jeff: Up to this point I don't believe the reader has seen a GPIS. We will replace the marker with a deterministic shape, but this figure gives a good idea of what we want to illustrate here.}}
\vspace*{-4ex}
\label{fig:grasp_model}
\end{figure}

\subsection{Sources of Uncertainty}
In this work we consider uncertainty in shape, pose, robot motion, and friction coefficient.
Fig. \ref{fig:graphical_model} illustrates a graphical model of the relationship between these sources of uncertainty.
In this section we describe each source of uncertainty and our model of the uncertainty.
We wish to emphasize that the models of uncertainty described in this work are not the only models that may be used with MAB algorithms and that the reader may choose parameters and distributions that best fit their needs, however performance is subject to vary on empirical results.

Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
Following ~\cite{laskey2015bandits, mahler2015gp} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
See Mahler et al.  for details on how to train a mean and covariance function and sample shapes from a GPIS \cite{mahler2015gp}.
In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.

\subsubsection{Pose Uncertainty}
In typical robotics applications the pose of objects in the environment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here

In 2-dimensional space, the pose of an object $T$ is a member of the Lie Group $SE(2)$.
This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:

One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$. \cite{barfoot2014Pose}.

 \subsubsection{Motion Uncertainty}
In practice a robot may not be able to execute a desired grasp plan $\Gamma$ exactly due to slight errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
In this work, we model motion uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
Formally, let $\hat{\by} = \frac{1}{2} (\ba + \bb)$ denote the center of a planned line of action $\gamma(t)$ and $\hat{\psi}$ denote the angle that the planned line $\bb - \ba$ makes with the x-axis of the 2D coordinate system on our shape representation.
Then the random center $\by \sim \mN(\hat{\by}, \Sigma_y)$ and the random angle $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
For shorthand in the remainder of this paper we will refer to the random motion parameters as $\rho = \{\by, \psi \}$.
In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.

\subsection{Grasp Quality}\label{sec:grasp_sample}
We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.

Formally, force closure is a binary-valued quantity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ... \bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{li1988task}.
In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
%\vspace{-2ex}
\begin{align*}
	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
\end{align*}

To estimate $P_F(\Gamma)$, we generate  samples from each of the above distributions in sequence using the relationships defined by the graphical model in Fig. \ref{fig:graphical_model}.To sample from $p_F(\Gamma)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule  we can rewrite this as

Mahler et al \cite{mahler2015gp}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). We then use these quantities to determine the grasp parameters $g$. Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.}
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

\subsection{Objective}

Given the sources of uncertainty and their relationships as described above, our goal is to find the grasp that maximizes the probability of force closure from a set of $P$ prespecified candidate grasps $\mG = \{\Gamma_1, ..., \Gamma_P\}$:

\vspace{-2ex}
\begin{align}
\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) 
\end{align}

Since we only can approximate the probability of force closure, with samples drawn from the distribution $P_F(\Gamma)$ our objective is rewritten as:

\vspace{-2ex}
\begin{align}
\Gamma^* &\approx \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
\end{align}

One method to solve Equation ~\ref{eq:problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grap plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}. In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem, which offers stronger theoretical and empirical performance \cite{agrawal2011analysis}\cite{chapelle2011empirical}.

\section{Multi-Armed Bandits for Grasp Selection}
\label{sec:MAB}
%While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we
We propose framing the problem in the multi-armed bandit (MAB) model and forming a policy for iteratively selecting which grasp to evaluate based on the probability of force closure estimate from the samples so far.
The goal of the MAB approach is to allocate more sampling effort to grasps that appear to have higher quality based on the evaluation performed so far.

@@

In a traditional MAB problem, a gambler has $K$ independent slot machines, or ``arms'' to play.
When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest reward and exploring new arms to see if they give better rewards on average.
Developing a policy that successfully trades between exploration and exploitation to maximize average reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.

Success in MAB problems is commonly measured in terms of {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.

>>>>

\title{\LARGE \bf
Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v5 Feb 18, 2015 ] }

\author{Michael Laskey$^1$, Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
}

@@

\begin{abstract}
\textit{Abstract---}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities. 
Monte-Carlo sampling is a popular approach to grasp planning under uncertainty, but it may require a large number of samples to converge, even for planar models.
We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.
We formulate grasp planning as a MAB  with finite stopping time to efficiently determine high quality grasp with respect to a probability of force closure metric.
To evaluate MAB-based sampling, we compare with two methods previously proposed for grasping an planar object under shape uncertainty represented as a Gaussian process implicit surface (GPIS) and Gaussian uncertainty in pose, grasp approach direction, and coefficient of friction.
%with shape uncertainty defined by a Gaussian process implicit surface (GPIS).
%Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
%Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
Our approach of using MAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
\end{abstract}

@@

Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
The robot may need to rapidly plan grasps, but may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.

% \begin{figure}%
%     \centering
% %     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%
% %       \qquad

%      \subfloat{{\includegraphics[width=8.5cm]{matlab_figures/pfc.eps} }}%

%     \caption{ Comparison of the current average probability of force closure vs. the stopping time $T_s$. The plots are averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with $|G|=1000$ for each shape.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach of Kehoe et al \cite{kehoe2012toward}. We also plot the average probability of force closure for the estimated optimal grasp evaluated using Monte-Carlo sampling. Empirically, it appears that Thompson and Gittins converge to the optimal solution at a faster rate, which is desired for an anytime algorithm.   }%
%     \label{fig:rot_shapes}%
% \end{figure}

\begin{figure}%
    \centering
     \subfloat{{\includegraphics[width=8.5cm, height=4.25cm]{figures/uncertainty_motivation.jpg} }}%

    \caption{ Illustration of the effects of pose and shape uncertainty on parallel-jaw grasps planned for a mechanical switch. Left: An RGBD camera observing the switch cannot detect the specular metal toggle and screw regions (black) and the average shape segmentation is rectangular. Middle: Optimizing the Ferrari-Canny quality on the estimated mean shape and pose results in an unstable grasp (red arrows) on the true object. Right: Selecting the grasp with the highest probability of force closure given shape and pose distributions chooses a stable grasp for the true object. \todo{Keep this new image or revert to old? Florian favored stronger motivation for uncertainty} }%
    \label{fig:motivation}%
\end{figure}

Analytic grasp quality metrics have been developed to plan grasps when all the parameters of the object and robot manipulator are exactly known.
One common measure of stability is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.
Grasps in force closure can be further ranked by the relative magnitude of forces and torques that must be exerted by the gripper to resist external perturbations~\cite{ferrari1992}.
Recent works have explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
One option is using Monte-Carlo Integration over the possible values of uncertain quantities to evaluate the probability of force closure for a grasp~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012estimating, kehoe2012towards}, but this can be computationally expensive.
In this work, we show that it is possible to rule out grasps with low probability of force closure in only a few samples and to allocate more sampling effort to grasps that are likely to be high quality.

The multi-armed bandit (MAB) model for sequential decision making~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} provides a formal way to reason about allocating sampling effort.
The MAB model is particularly useful in applications where it is too expensive to fully evaluate a set of options; for example, in optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.
In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution.
The goal in a MAB problem is to  select a sequence of options to maximize expected reward. \todo{explain why} The MAB algorithms can be interpreted as an anytime algorithms, where at a provided stopping time the algorithm terminates and returns the estimated best grasp with respect to a chosen metric.

We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem.
We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, grasp approach direction, and friction coefficient. 
We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}. 
We model uncertainty in pose as a normal distributions around the orientation and translation of the object.
Uncertainty in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.

We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, for selecting grasps with high probabilty of force closure on the Brown Vision 2D Dataset~\cite{brown, christopoulos2007handling}, a dataset of over 1000 planar objects.
\todo{Get within 5 of best value numbers}
Initial results over 100 shapes suggest that on average the grasp return after a given stopping time on the number of samples is of higher quality than that of previous methods.

@@

Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, and uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}. One method to represent pose uncertainty is to place a normal distribution around the location of the center of the object as well as the rotational component of the object \cite{barfoot2014Pose}. This approach is easy to sample from in the planar case, since each sample is from a fixed 3D Multivariate Gaussian.

For shape uncertainty we used a Gaussian process implicit surface representation. 
Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.

One common method for evaluating a probabilistic grasp quality measure is to use Monte-Carlo sampling~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}, which involves sampling from distributions on random quantities and averaging the quality over these samples to empirically estimate a probability distribution\cite{caflisch1998monte}. It can be computationally expensive though to sample all proposed grasps to convergence.  To  address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of samples needed in Monte-Carlo sampling to choose the highest quality grasps. However, the proposed adaptive sampling approach pruned grasps using only the sample mean and did not utilize any estimates variance around the current estimate, which in practice could lead to good grasps being thrown away. We propose treating the problem as an Multi-Armed Bandit, which instead of pruning grasps away decide based on past observations what grasp to sample next \cite{barto1998reinforcement}.

@@

In a traditional MAB problem, a gambler has $K$ independent one-armed bandits, also known as slot machines.
When an arm is played (or ``pulled'' in the literature), it returns an amount of money from a fixed reward distribution $P_k, k = 1, ..., K$ that is unknown to the gambler.
The goal of the gambler is to come up with a method for determining which arms to pull, how many times to pull each arm, and what order to pull them in such that the average cumulative rewards are maximized over many pulls.
If the gambler knew the machine with the highest expected reward, the gambler would only pull that arm.
However, since the reward distributions are unknown, a successful gambler needs to trade off exploiting the arms that currently yields the highest reward and exploring new arms to see if they give better rewards on average.
Developing a policy that successfully trades between exploration and exploitation to maximize average reward has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.

At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the arm selected. Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
%Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
Since then a several other algorithms have been shown to achieve near this bound in terms of convergence, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.

\subsection{Algorithms for MAB}\label{sec:bandit_algorithm}
We consider Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) ~\cite{chapelle2011empirical, bachman2013greedy}. Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving near the lower bound on the asymptotic rate of convergence in regret described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.

Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank. For instance a Bernoulli random variable, $\theta$, can be used to represent a binary grasping metric like force closure. The prior traditional placed on a Bernoulli variable is its conjugate prior the Beta distribution. 
Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).

%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
%See \cite{} for a review of bayesian methods in multi-armed bandit problems.
